### 2021-06-07 paper/calibration_and_estimation.tex
Moved on with description of Fig. 3.

Figure~\ref{fig:assortativity} shows that assortativity by age is especially strong for
children and younger adults. For older people, the pattern becomes more dispersed around
their own age group, but within-age-group contacts are still the most common contacts.

>>>>

Figure~\ref{fig:assortativity}\comment[id=HM]{So no work in here? How about school? Can we add a column with marginals and another one with work / (school?), too?} shows that assortativity by age is especially strong for
children and younger adults. For older people, the pattern becomes more dispersed around
their own age group, but within-age-group contacts are still the most common contacts.

### 2021-06-07 paper/report.tex
Moved on with description of Fig. 3.

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-left}
        \caption{{\small Model description}}
        \label{fig:broad_model_description}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-right}
        \caption{Disease progression}
        \label{fig:disease_progression}
    \end{subfigure}
    \vskip3ex
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/model-graph-bottom-left}
        \caption{{\small PCR and antigen tests}}
        \label{fig:pcr_antigen_tests}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

@@

    \floatfoot{
        Note: ...
    }

@@

    \floatfoot{
        Note: All aggregates; See S.XXX for statistics by age group and by geographical region. Also more disaggregated data.

@@

These developments are characteristic of many countries: The inititial focus on NPIs to
slow the spread of the disease has been accompanied by vaccines and a growing acceptance
and use of rapid tests. At broadly similar points in time, novel strains of the virus
have started to pose additional challenges. The blue line in
Figure~\ref{fig:aggregated_fit} shows that our model tracks the simulated infections
extremely well. This is also true for infections by age and geographical region, which
are shown in the supplementary materials (S.\comment[id=HM]{reference}). We can
disentangle various mechanisms due to the distinct temporal variation in the drivers of
the pandemic. Next to the stringency index, the three lines in
Figure~\ref{fig:stringency_index} summarize how contact reductions, increased hygiene
regulations, and seasonality evolved since early September for each of the three broad
contact networks. For example, a value of 0.75 for the work multiplier means that if the
environment was the same as in September (levels of infection rates, no rapid tests or
vaccinations, only the wildtype virus present), infections at the workplace would be
reduced by 25\%. This reduction is the product of the effect of contact reductions,
increased hygiene regulations, and seasonality. Along with the levels of infections,
these measures completely determine the spread of SARS-CoV-2 in
2020.\comment[id=HM]{True?} See Appendix~\comment[id=HM]{Reference} for their individual
contributions. Two things are particularly interesting. First, all lines broadly follow
the stringency index and they would do so even more if we left out seasonality. Second,
the most stringent regulations are associated with the period of strong decreases in new
infection beteen late December 2020 and mid-February 2021. The measures were not enough,
however, to stop the B.1.1.7 variant from spreading in the subsequent period. The steep
drop in recorded cases during May 2021 is associated with rapid tests to X-Y~percent of
the population, a vaccination rate that rose from 25\% to 4X\%, and mostly seasonality
impacting a fall in the relative infectiousness of contacts.

Reassured by good fit and a couple of external checks (fall vacation regression?),
Figure~\ref{fig:2021_scenarios_broad} consider the relative effects of rapid tests,
vaccinations, and of seasonality during 2021, assuming NPIs to be the same as in the
baseline scenario. Figure~\ref{fig:2021_scenarios_recorded} shows the model fit (blue
line, same as in Figure~\ref{fig:aggregated_fit}), a scenario without any of the three
factors (x line), and three scenarios turning these factors off one by one.

@@

    \floatfoot{
        Note: All aggregates; See S.XXX for statistics by age group and by geographical region.

@@

@@

    \floatfoot{
        Note: All aggregates; See S.XXX for statistics by age group and by geographical region.
    }

>>>>

    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-left}
        \caption{{\small Model description}}
        \label{fig:broad_model_description}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-right}
        \caption{Disease progression}
        \label{fig:disease_progression}
    \end{subfigure}
    \vskip3ex
    \begin{subfigure}[b]{0.425\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/model-graph-bottom-left}
        \caption{{\small PCR and antigen tests}}
        \label{fig:pcr_antigen_tests}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering

@@

    \floatfoot{\noindent
        Note: ...
    }

@@

    \floatfoot{\noindent
        Note: All aggregates; See S.XXX for statistics by age group and by geographical region. Also more disaggregated data.

@@

These developments are characteristic of many countries: The inititial focus on NPIs to slow the spread of the disease has been accompanied by vaccines and a growing acceptance and use of rapid tests. At broadly similar points in time, novel strains of the virus have started to pose additional challenges. The blue line in Figure~\ref{fig:aggregated_fit} shows that our model tracks the simulated infections extremely well. This is also true for infections by age and geographical region, which are shown in the supplementary materials (S.\comment[id=HM]{reference}). We can disentangle various mechanisms due to the distinct temporal variation in the drivers of the pandemic. Next to the stringency index, the three lines in Figure~\ref{fig:stringency_index} summarize how contact reductions, increased hygiene regulations, and seasonality evolved since early September for each of the three broad contact networks. For example, a value of 0.75 for the work multiplier means that if the environment was the same as in September (levels of infection rates, no rapid tests or vaccinations, only the wildtype virus present), infections at the workplace would be reduced by 25\%. This reduction is the product of the effect of contact reductions, increased hygiene regulations, and seasonality. Along with the levels of infections, these measures completely determine the spread of SARS-CoV-2 in 2020.\comment[id=HM]{True?} See Appendix~\comment[id=HM]{Reference} for their individual contributions. Two things are particularly interesting. First, all lines broadly follow the stringency index and they would do so even more if we left out seasonality. Second, the most stringent regulations are associated with the period of strong decreases in new infection beteen late December 2020 and mid-February 2021. The measures were not enough, however, to stop the B.1.1.7 variant from spreading in the subsequent period. The steep drop in recorded cases during May 2021 is associated with rapid tests to X-Y~percent of the population, a vaccination rate that rose from 25\% to 4X\%, and mostly seasonality impacting a fall in the relative infectiousness of contacts outside of work and school\comment[id=HM]{check with corrected graph}.

Figure~\ref{fig:2021_scenarios_broad} consider the relative effects of rapid tests, vaccinations, and of seasonality during 2021, assuming NPIs to have evolved the same way as in the baseline scenario. Figure~\ref{fig:2021_scenarios_recorded} shows the model fit (the bold blue line\comment[id=HM]{Make sure this is the case}, same as in Figure~\ref{fig:aggregated_fit}), a scenario without any of the three factors (x line), and three scenarios turning these factors off one by one. Figure~\ref{fig:2021_scenarios_newly_infected} does the same for total infections in the model. Figure~\ref{fig:2021_scenarios_decomposition} employs Shapley values to decompose the difference in total infections between the scenario without any of the three factors and our main specification.

@@

    \floatfoot{\noindent
    Note: All aggregates; See S.XXX for statistics by age group and by geographical region.

@@

The effect of the vaccination campaign is surprisingly small at first sight. The reasons for this are the slow start---10\% of the population was vaccinated in XX date, 20\% in mid-April\comment[id=HM]{(check!)}---and the focus on older individuals. These groups contribute less to the spread of the disease than others due to a lower number of contacts, see~\ref{fig:assortativity}. It is important to note that the initial focus of the campaign was to prevent deaths and severe disease; the case fatality was rate considerably lower during the third wave when compared to the second.\comment[id=HM]{Calculate N deaths / N cases, for RKI data 1 October - 31 Jan vs. 1 Mar - 31 May}.

\clearpage

\section*{writing barrier}

@@

    \floatfoot{\noindent
        Note: All aggregates; See S.XXX for statistics by age group and by geographical region.
    }
